\chapter*{Acknowledgment}
\pagestyle{plain}
%\addcontentsline{toc}{chapter}{\protect\numberline{}{Dedication}}
%\addtotoc{Acknowledgment}

First I would like to thank almighty Allah for giving me the strength to complete this thesis. The journey is completed for those two people without their help it is impossible to complete my works are my supervisors Professor Tapabrata Ray and Lecturer Hemenat Kumar Singh. I can not forget their initial nursing to make me suitable to do research. 

The Journey Started on 01 March, 2014 with lots of anxiety, ambition  and loneliness. Without some people it was unimaginable to me to survive. I would like to thank Md Shaker Ullah Chowdhury and Md Sharif Khan for their warm reception and hospitality.   Md Asafufddoula, Yunus Khan and Sayem vi gave the place to live for the first three weeks. Special thanks for them from my heart. I am thankful to a person who initially play the role as a advisor is Md Shahidul Islam. Special thanks to suborna apu, Sadia apu, Liza vabi, Khairul vi,Rajib vi, Simi apu, Azam vi, Shiblee, Moon, Jahnagir Vi, Jamil sir, Karim vi  and  many others for their frequent invitation and mental support.There are no words for those people which i can use to complement them.

I am so lucky to have such a community to spend time here with full pleasure. Lot of name arises without them, I can not imagine Canberra life. Some of them include Habibullah, Polash, Fahad, Fuad, Mohiuddin, Sumon, Monir, Kalyan da, Smita apu, Mehedi vi, Ripon da, Forhad vi, Atik, Sadat, Perli, Kader vi, Bashir vi(Phd mate), Ashraf vi, Jahid vi, Khaleq vi, Tanmoy, Nargis apu, Shahin vi, Alamgir, Barik vi, Hafiz vi, Mahi,Jyoti, Obina, Iroizen, Rashed, Rocky, Rupom da, Sumona, Safin, Sanjoy da, Shakayat vi, Shohrab, Sohel vi, Sukanta da, Tanmoy and many others which I can not count. My heartfelt thanks to all who helps me in many ways in my Canberra life. My apologies to all of them whose name are not listed in the list.  

I cannot forget the MDO groups contributions to complete my journey. At the very beginning Md Asafuddoula gave nice briefing to introduce me in Optimization. In the later phase continuous guidance from Professor Ray and Dr. Hemant are really can not count in words . Specially several meetings in a day were really helped me to improve my knowledge. Special thanks to Hemant for excellent guidance as a supervisor in coding correction, correction on writing and many others things related to research. Special Thanks to Kalyan, Shiblee, Shelvin, Khairul Vi and Quang for their continuous supports in many ways in difficult times.

I am really thankful to some guys for their mental support while I was extremely sick in Australia. My grateful thank to my supervisors Professor Ray and Lecturer Hemant for their co-operation, economic support and great humanity. Habiibullah, kalyan da, Kalyan, Monir, Smita Apu, Mehedi Vi, Shaker vi, Suborna Apu, Shohrab  were so good which helped me to survive on my bad situation.


I am lucky to get such a adorable family members including my younger sister Nurjahan, Nasrin, borther Monoarul and brother-in law Anis, Niece Sarah. I have got a new family during my Phd life contains my father in-law, mother-in law, Rine apa, Asad dulavi and Adiba. I would like to give them thank for their continuous support on my work.

I am so much grateful to my lovely wife Saiba Nazah for giving me continuous support in every situation. Without her encouragement it was really impossible for me to mange all the things perfectly.
At last I have no words to thank two people without them I can not able to seen the world is my parent. My lifetime effort to make them little happy is nothing compared to their support, sacrifice and love they give me. I want to dedicate my thesis to these two beautiful person in the world. 